Midyear Performance vs Projection

### 2019-07-06 midyear_perfVsProj.Rmd
Latest rosters

#Manually loading latest performance from fangraphs
pitcher_perf <- "temp/FanGraphs Leaderboard.csv" %>% 
  add_z_scores("pitcher") %>% 
  clean_names() %>% 
  select(type, playerid, name:so,era:war, z_sv:z_sum) %>% 
  mutate(playerid = as.character(playerid))

>>>>

#Manually loading latest performance from fangraphs
pitcher_perf <- "temp/FanGraphs Leaderboard - perf.csv" %>% 
  add_z_scores("pitcher") %>% 
  clean_names() %>% 
  select(type, playerid, name:so,era:war, z_sv:z_sum) %>% 
  mutate(playerid = as.character(playerid))
